Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-02 document/ms.tex
Small typos and additional text for figure caption for the manuscript

\begin{figure*}
	\centering
	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
	\caption{\name $V-$band photometric monitoring from 1986$-$2016.  The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.  The near contemporaneous DoubleSpec and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.  The abscissa range is equal to the current lifespan of the first author of this paper.}
	\label{fig:PhotTime}
\end{figure*}

@@

The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $c$.  The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.  So the second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.  The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.  The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.  So stellar parameter estimates $\vT_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.  The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or clear model mismatches.  This process can be thought of as a course approximation to the much more sophisticated spectral line outlier rejection described in \iancze.

@@

We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth spectrum from Table \ref{tbl_estimated_V}.  The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.  Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.  The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/single_Teff_v_order}
	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum assuming a single component photosphere.  }
	\label{fig:SingleTeffvsOrder}
\end{figure*}

@@

Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Sectrion \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [-3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.  The MCMC chains all appeared to converge after about 1500 steps.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
	\caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.  The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.  The near contemporaneous DoubleSpec and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.  The abscissa range is equal to the current lifespan of the first author of this paper.}
	\label{fig:PhotTime}
\end{figure*}

@@

The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $c$.  The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.  So the second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.  The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.  The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.  So stellar parameter estimates $\vT_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.  The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.  This process can be thought of as a coarse approximation to the much more sophisticated spectral line outlier rejection described in \iancze.

@@

We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V}.  The spectrum was apportioned into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.  Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.  The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/single_Teff_v_order}
	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.  The top panel indicates the location and size of spectral chunks used to derive the values in the bottom panel.  The IGRINS orders also show typical atmospheric transmission (red lines) in the infrared.  Unused spectral chunks are lightened.  The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.}
	\label{fig:SingleTeffvsOrder}
\end{figure*}

@@

Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Sectrion \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.  The MCMC chains all appeared to converge after about 1500 steps.
